\begin{abstract}
  Modern programming follows the continuous integration (CI) and continuous
  deployment (CD) approach rather than the traditional waterfall model.  Even
  the development of modern programming languages uses the CI/CD approach to
  swiftly provide new language features and to adapt new development
  environments.  Unlike the conventional approaches, in the modern CI/CD
  approaches, the language specification is no more the Oracle of semantics
  because both the specification and interpreters (or compilers) can co-evolve.
  In this setting, both the specification and implementations may have bugs, and
  guaranteeing their correctness is non-trivial.

  In this paper, we present a novel \textit{$N$+1-version testing} to resolve
  the problem.  Unlike the traditional $N$-version testing, our approach
  consists of three steps: 1) to automatically synthesize programs guided by the
  syntax and semantics from the given language specification, 2) to generate
  conformance tests by injecting assertions to them to check their final program
  states, and 3) to find and localize the specification bugs via executing
  programs on multiple implementations.  We propose \( \tool \) that performs
  $N$+1-version testing for modern JavaScript engines and ECMAScript, which is
  the specification of JavaScript that describes syntax and semantics in a
  natural language.  We evaluated our tool with four JavaScript engines that
  support all modern JavaScript language features and the most recent version of
  ECMAScript (ES11, 2020).  \( \tool \) automatically synthesized \inred{X,XXX}
  programs that covered \inred{XX.XX\%} of syntax and \inred{XX.XX\%} of
  semantics from ES11.  Using the assertion-injected JavaScript programs, our
  tool found \inred{XX} engine bugs in four different engines and \inred{X}
  specification bugs in ES11.
\end{abstract}
